There once was a grid at ol' Carkeek

### 2016-03-15 Manuscript/carkeek_grid.tex
add to intro and methods

@@

Where $\beta_0$ is a general intercept across all taxa, $\beta_i$ is a fixed effect accounting for the variance associated with taxon $i$, and $\eta_{ijk}$ and $\epsilon_{ijk}$ are random effects of variance resulting from the processes associated with PCR and spatial location, respectively.

@@

>>>>

We would love to estimate the minimum distance over which eDNA community differences can be detected.

@@

%(\ref{my_equation_label})
Where $\beta_0$ is a general intercept across all taxa, $\beta_i$ is a fixed effect accounting for the variance associated with taxon $i$, and $\eta_{ijk}$ and $\epsilon_{ijk}$ are random effects of variance resulting from the processes associated with PCR and spatial location, respectively.

Sidenote justification for k-means clustering: While variation among sampled ecological is indeed continuous, ecologists often apply categorical groupings to ecological communities.
For example, we may sample along a transect that intersects rainforest and desert.
As our samples become smaller and closer together, we may have increasing difficulty assigning samples to a distinct habitat type.

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{site_map.pdf}
    \caption{Geographic position of collected samples. Lines give 10m isobaths.}
  \label{site_map} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{clustering_fig.pdf}
    \caption{Plot of ?(non-metric multi-dimensional scaling | principal components ) analysis. Points are colored by their membership to clusters of k-means clustering analysis.}
  \label{clustering_fig} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{dissim_by_distance.pdf}
    \caption{Pairwise dissimilarity ?(BRAY CURTIS/ETC) of eDNA communities plotted against pairwise spatial distance.}
  \label{dissim_by_distance} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{slope_plots.pdf}
    \caption{Fit lines of DNA sequence counts as a function of distance from shore for a selection of taxa for which we have strong preconceived expectations (left). Box plots of the estimates of the slopes for taxa ?(100 most abundant)?, grouped by life history traits (right).}
  \label{slope_plots} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{var_boxplots.pdf}
    \caption{Box plots of estimates of variance associated with each level of the multilevel model, corresponding to stages of the eDNA sampling protocol.}
  \label{variance_boxplots} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{clustering_map.pdf}
    \caption{Geographic position of collected samples, colored by membership to clusters identified by k-means clustering analysis. Lines give 10m isobaths.}
  \label{clustering_map} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}
